STatistical Computing (MATH6173) Coursework 2

### 2022-12-17 draft_report.Rmd
Starting on creating final R code script (Finished initial add of Q1,4 and 5)

pi.x <- function(x){
  pi <-NULL
  for (i in 1:length(x)){
  if (x[i]>1.25){
    pi[i] <- (2*1.25^(2))/(2*x[i]^(3))
  } else if (x[i] >= -1.75){
    pi[i] <- 1/6
  }else{
    pi[i] <- 0
  }
  }
  return(pi)
}

@@

plot(x=x,y=pi.x(x),
     type="l",
     ylab = "density",
     main="Plot 1: Comparing target and proposal pdf's",
     sub="Note: used a=2,b=3,s=1.25 with the green line seperating the regions of the graph")
curve(gx.1(x),add=T,col="red")
curve(gx.2,add=T,col="blue")
abline(v=-1.75,lty=2,col="green")
abline(v=1.25,lty=2,col="green")
text(x=-3,y=0.4,labels="Region 1")
text(x=0,y=0.4,labels="Region 2")
text(x=6,y=0.4,labels="Region 3")
legend("topright", lty = c(1,1,1), cex = 0.6, col = c("black","red","blue"),
legend = c("Target distribution pdf","g(x) pdf with lambda=1","g(x) pdf with lambda=0.5"))
```

>>>>

target.dist<- function(x){
  pi <-NULL
  for (i in 1:length(x)){
  if (x[i]>1.25){
    pi[i] <- (2*1.25^(2))/(2*x[i]^(3))
  } else if (x[i] >= -1.75){
    pi[i] <- 1/6
  }else{
    pi[i] <- 0
  }
  }
  return(pi)
}

@@

plot(x=x,y=target.dist(x),
     type="l",
     ylab = "density",
     main="Plot 1: Comparing target and proposal pdf's",
     sub="Note: used a=2,b=3,s=1.25 with the green line seperating the regions of the graph")
curve(gx.1(x),add=T,col="red")
curve(gx.2,add=T,col="blue")
abline(v=-1.75,lty=2,col="green")
abline(v=1.25,lty=2,col="green")
text(x=-3,y=0.4,labels="Region 1")
text(x=0,y=0.4,labels="Region 2")
text(x=6,y=0.4,labels="Region 3")
legend("topright", lty = c(1,1,1), cex = 0.6, col = c("black","red","blue"),
legend = c("Target distribution pdf","g(x) pdf with lambda=1","g(x) pdf with lambda=0.5"))
```
